\bf Landslide: Systematic Testing in 15-410 \\ Sign-Up Sheet

### 2015-02-10 irb/hurdle.tex
More changes to signup, solicitation, lecture

Thanks for volunteering to try out Landslide! To participate in the study, you and your partner must meet all the prerequisites below. Submit this form at my office (GHC 9009), any weekday between 13:00 and 17:00, or if you can't make it during those times, scan it after signing and email to {\tt bblum@cs.cmu.edu}.
\\

@@

\end{tabular}
\\
\vspace{0.5in}
\\
Group number: \underline{\hspace{1.5in}}\\
\vspace{0.5in}\\
Partner 1 andrewid: \underline{\hspace{1.5in}} Signature: \underline{\hspace{1.5in}} Date: \underline{\hspace{1in}}\\
\vspace{0.5in}\\
Partner 2 andrewid: \underline{\hspace{1.5in}} Signature: \underline{\hspace{1.5in}} Date: \underline{\hspace{1in}}

>>>>

Thanks for volunteering to try out Landslide! To participate in the study, you and your partner must meet all the prerequisites below. Submit this form at my office (GHC 9009), any weekday between 13:00 and 17:00, or if you can't make it during those times, scan it or take a picture after signing and email to {\tt bblum@cs.cmu.edu}.
\\

@@

\end{tabular}
\\
\vspace{0.5in}
\\
Group number: \underline{\hspace{1.5in}}\\
\vspace{0.5in}\\
Partner 1 Andrew username: \underline{\hspace{2.5in}} Date: \underline{\hspace{1.5in}}
\vspace{0.5in}\\
Partner 2 Andrew username: \underline{\hspace{2.5in}} Date: \underline{\hspace{1.5in}}
